%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
% Document margins
\usepackage[colorlinks]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\custom}[1]{\hspace{0em}\rlap{#1}}
\name{Uday Kumar Mydam} % Your name
%\address{13th B Cross Rd, 6th Main Rd, Teacher's Colony, HSR Layout 5th Sector, Bengaluru, Karnataka 560034, India} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{{\bf Mobile}: +91-9849845634    \\ {\bf Email}: uday.mydam@gmail.com} % Your phone number and email
\begin{document}
\begingroup%
\hypersetup{urlcolor=blue}%
{\hspace{30ex}}\href{https://github.com/uday4393/}{Github://uday}%
{\hspace{5ex}}\href{https://www.linkedin.com/in/udaykumarmydam/}{LinkedIn://uday}%
\endgroup
\\
%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Summary}
Passionate Fullstack Developer with 8+ years crafting innovative solutions in major tech stacks. Proven track record in delivering high-quality applications, from conceptualization to deployment. Seeking challenging opportunities to apply my technical acumen and drive innovation in dynamic environments.
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf National Institute of Technology, Warangal}\hfill {\bf 2011 - 2015} 
\\B.TECH \hfill { CGPA: {\bf 8.32}/10}
\\ Department of Electronics and Communication Engineering \\
\end{rSection}
%----------------------------------------------------------------------------------------
%	AREAS OF INTEREST SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{AREAS OF INTEREST}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Data Analysis {\hspace{4ex}} Data Structures  {\hspace{2ex}}  Algorithm and Computations{\hspace{2ex}} Design Patterns \\ {\hspace{9ex}}Machine Learning{\hspace{2ex}}Database Management{\hspace{2ex}}

%\end{tabular}

% \end{rSection}
\begin{rSection}{Technical Expertise}
TypeScript, JavaScript, Python, Java, C/C++, NodeJS, Express, React, 
Angular10+, MEA/RN Stack, VueJS, SA/CSS, Tailwind, Bootstrap, GraphQL,
Docker, Kafka, Kubernetes, Jenkins, Datadog, ChaosSearch, AWS, PostgresSQL, MongoDB, Redis, MicroServices, Serverless, ChatGPT, Generative AI,
GitHub, Babel, TDD Frameworks(Jest, Karma, Mocha), Agile, JIRA, Springboot, Gradle.
\end{rSection}
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL EXPERIENCE}
\setlength{\itemindent}{-.1in}

\item[1.]\begin{rSubsection}{Software Engineer - Klarna, Stockholm }{\bf |Aug 22 - current}
{{\bf}}{}
\item[$\Rightarrow$] Delivered Highly Scalable products as part of the Customer Services Domain at Klarna which is the main backbone of all things related to Tooling to the agents which enables great customer service.
\item[$\Rightarrow$] Instrumental in the customer service domain, I spearheaded a GPT-based Initiative aimed at minimizing dispute errand rates and alleviating backlog, resulting in substantial cost savings. As the sole backend developer, I effectively liaised with stakeholders, turning a highly successful proof of concept into a profitable venture, saving millions of SEK.
\item[$\Rightarrow$] Designed and Implemented History Service which track fradulent agent actions.
\item[$\Rightarrow$] Worked on Lakehouse Integration with Terraform(IaC) for Analytics purposes.
\item[$\Rightarrow$] As a key contributor in Klarna's Instore domain, I focus on Scan Partner QR, engaging in discovery, analysis, and roadmap planning. My role within the Global Klarna Distribution API involves efficient delivery, predominantly utilizing Java for robust backend development.
\end{rSubsection}
\vspace{1em}

\item[2.]\begin{rSubsection}{Senior Software Engineer - CHUBB Insurance, Hyderabad}{\bf |Aug 20 - Nov 21}
{{\bf}}{}
\item[$\Rightarrow$] Lead, Deliver the Project to stakeholders, Mentor and guide junior developers.
\item[$\Rightarrow$] Successfully Delivered two projects on an acceptable timeline without compromising the Quality of the product.
\item[$\Rightarrow$] Design, Architect the solutions, Follow Agile process and Quality Standards.
\item[$\Rightarrow$]UDA - Underwriter's Digital Assistant - is an Angular 10+ SPA collating data from all API endpoints such as Google maps, P360, Tensor flight data, and various other internal data sources that are fed through a NodeJS Backend Server using latest libraries.
\item[$\Rightarrow$] DnO - Directors' and officers' Insurance Liability Dashboard -- It is an Angular 10+ SPA with Node back-end pumping data via Azure Cosmos DB.
\end{rSubsection}
\vspace{1em}
\item[3.]\begin{rSubsection}{Senior Software Developer - Swap Motors, Hyderabad}{\bf |June 2018 - Aug 2020}
{{\bf SwapMotors - Product Development}}{}
\item[$\Rightarrow$] Swapmotors is a Chicago-based startup disrupting Used-car Industry in the US. The USP is that it uses two channels Auction and Marketplace to sell cars to users.
\item[$\Rightarrow$] It's a website-based product that uses VueJS frontend, nodeJS backend, and MongoDB, AWS for storage solutions.
\item[$\Rightarrow$]I am part of the India development team, working actively in both the frontend and backend parts of the application.\\
\end{rSubsection}
\vspace{0.5em}
\item[4.]\begin{rSubsection}{Software Developer - Wipro Technologies, Bangalore}{\bf |Dec 2015 - June 2018}
{{\bf Federated Search Project}}{}
\item[$\Rightarrow$]Client(EA Inc.) was migrating to new Intranet service using LUMAPPS. I, as part of backend team was responsible for Intranet Search, a Node based service which included results from various sources of internal sites, their game engine (Frostbite), various external sources that orchestrates and acts as an abstraction layer.
\item[$\Rightarrow$]{Skills used: AWS, Serverless, NodeJS, Cloud Formation template, Testing frameworks.}\\
\end{rSubsection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Responsibilities} \itemsep -1pt
\item[$\Rightarrow$] Ownership of the product, Design Product Road Map, Delivery Timelines, Quality Standards.
\item[$\Rightarrow$] Participate and Lead the team in Product analysis, Design decisions, and Architectural decisions.
\item[$\Rightarrow$] Guiding, Mentoring developers technically, and participating in the hiring process. 
\item[$\Rightarrow$] Ensuring and implementing Agile Scrum, transforming User stories into technical features.
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
%\newpage
\begin{rSection}{PROJECTS}
\setlength{\itemindent}{-.2in}
\item[1.]\begin{rSubsection}{GRADUATION THESIS---NIT, WARANGAL}{\bf |Jan - May 2015}
{{\bf}}{}
\item[$\Rightarrow$]Implemented in Security domain as a final year project titled “Simulation of Packet Filtering Engine on FPGA Device”. Implemented various algorithms for Data encryption techniques including \textbf{AES256bit} and RSA in C language.Implemented models for WEP and WPA in NS3 software.
\end{rSubsection}
\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Achievements} \itemsep -2pt
% \item[$\Rightarrow$] Received Best Performer Award in CHUBB 2021.
% \item[$\Rightarrow$] Received Rising Star Award in Wipro 2016.
% \item[$\Rightarrow$] Ranked in National Top 1\% (amongst 1,200,000 candidates) in {\bf JEE Mains 2011}.
% \end{rSection}

\end{document}
